\documentclass[12pt]{article}

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage{url}
\usepackage{minitoc}

\usepackage[left = 1cm, top = 2cm, bottom = 3cm, right = 1cm]{geometry}

\newcommand{\XB}{\color{black}}
\newcommand{\XBB}{\color{blue}}
\newcommand{\XV}{\color{violet}}
\newcommand{\XR}{\color{red}}
\newcommand{\ds}{\displaystyle}

\setcounter{secnumdepth}{0}

\begin{document}

\title{\textbf{CSC517}: Social Computing - \\ Networks in Surrounding Contexts}
\date{\today}
\author{\XV\textit{\large{\href{https://github.com/casonk}{Cason Konzer}}}\XB}

\maketitle
\hrulefill
\vfill 

\pagebreak

\tableofcontents
% \listoftables
% \listoffigures

\newpage

\section{Narrative Summary}
To describe my historical networks I find it best to represent a social-affiliation network. 
The mains focal points I will examine are: Middle School, High School, School District, and Ski Resort. 
As networks evolve overtime, this report will be temporal in nature. 

When in middle school, my friends were gained thorough focal closure, with middle school being the focal point; the middle school joined 3 elementary schools (exposing me to many new faces). 
Additionally, during middle school a structural change was imposed which joined 3 classes, rather than 2 as in my first year. 
Accordingly, thorough the act of insult, I met Insulter in the hallways, an upperclassman which poked fun of my purple shirt. 
As children do, I promptly fired an insult back and we quickly became friends through selection. 

Surprisingly, we later found common affiliation at ski resort, and spent many weekends causing trouble together. 
Through these weekend hangs I was quickly exposed to many other upperclassmen and grew my network with them, via triadic closure. 
One of these individuals was Triad who is a prime example to illustrate membership closure. 
As both myself and Insulter were spending many winter days at ski resort, it was not long before Triad took up skiing.

Promptly, both Insulter and Triad knew upperclassmen to themselves also affiliated with ski resort which I became friends through a combination of focal and triadic closure. 
As a result, it was not long before, through social selection, hanging with underclassmen was `not cool' and I quickly pruned many of my previous class friends. 
Generally speaking, this change happens as Insulter and Triad stepped into high school. 
Granted, selection drove the exception such that if an underclassmen was affiliated with ski resort, then they had a general in and were considered `cool.'
In this manner the affiliation of school district quickly dissolved, which persisted as I became a member of high school. 

Still, some fiends were kept from school district, not in affiliated with ski resort, as did most teenagers at the resort. 
Building on this phenomena, from the perspective of an affiliation network, my friend group was extremely diverse. 
A driving factor was locality, in which many affiliations where held as interdistrict clubs or sports. 
Lastly, this explains a low neighborhood overlap of individuals affiliated with ski resort. 

In summary, my historical network exhibited homophily, thorough a variety of driving phenomena, with focus on skiing.

\end{document}